\section{Related work}
\label{sec:related}

\paragraph{Event-sequence and tabular transformers.} Encoder-only, masked-pretrained
transformers~\cite{vaswani2017attention,devlin2019bert} over tokenised tabular/event sequences are
well established: BEHRT for medical records~\cite{li2020behrt} and TabBERT/TabFormer for
transactions~\cite{padhi2021tabular} introduced the hierarchical field-then-sequence design our
backbone follows, and related tabular transformers add contextual and row-attention
encodings~\cite{huang2020tabtransformer,somepalli2021saint,gorishniy2022embeddings}. The neural
architecture we build on is therefore not itself novel; our object of study is what the
\emph{two-attention} recipe misses relationally, and how to add it cheaply.

\paragraph{Industrial financial foundation models.} Two recent industrial systems are the closest
prior work. PRAGMA~\cite{ostroukhov2026pragma} pretrains a masked transformer on heterogeneous
banking event sequences and serves credit scoring, fraud, and lifetime-value prediction from one
representation read by a linear probe or a light fine-tune --- the recipe we reproduce at
laptop scale. TREASURE~\cite{yeh2025treasure} encodes payment-network transactions with dedicated
static/dynamic modules and ingests payment-network signals alongside consumer behaviour. Both encode
a \emph{single entity's own event stream}; neither reads, at inference, the concurrent activity of a
shared entity across \emph{other} accounts. Our cross-sequence attention is orthogonal and composable
--- it augments such a backbone rather than replacing it.

\paragraph{Adaptation: probing vs.\ fine-tuning.} Adapting a pretrained encoder ranges from a frozen
linear probe over its embeddings to full fine-tuning. A frozen probe measures what the
self-supervised objective already preserved; fine-tuning lets the task reshape the backbone. We use
both as baselines and show that the relational signal is recovered only when the third attention is
present, whether frozen features are read or the backbone is fine-tuned.

\paragraph{GBDTs for fraud.} Gradient-boosted trees~\cite{ke2017lightgbm,chen2016xgboost} with
client- and entity-level aggregate features remain the production and competition standard for
tabular fraud, and are a demanding baseline; we compare against a strong GBDT given per-entity causal
aggregates on the identical evaluation subsample.
