\section{Controlled synthetic benchmark}
\label{sec:synthetic}

To remove every confound we generate transactions where we \emph{know} where the fraud signal
lives. Two mechanisms: \textbf{per-account} --- a card is compromised and fires a short burst of
fraud on its own timeline (a per-sequence signal); \textbf{relational} --- a merchant is
compromised for a short window, producing a velocity spike of fraud across \emph{many random
cards}, with fraud amounts drawn from the legit distribution, a uniform per-merchant fraud rate
(so merchant identity is uninformative), and random fraud cards (so no per-card-history tell). The
only signal is the merchant's transient cross-card velocity. A LightGBM feature-group ablation
confirms the design: per-account fraud is recovered by card history (PR-AUC $0.04\!\to\!0.82$) and
invisible to merchant velocity; relational fraud is invisible to card history ($0.06$) and
recovered \emph{only} by cross-entity windowed velocity ($0.06\!\to\!0.36$).

\paragraph{Structural blindness and the proxy-alignment gap.} A frozen-probe FFM \emph{nails}
per-account fraud (PR-AUC \num{0.81}) and \emph{collapses to base} on relational fraud
(\num{0.035}) --- same model and data, opposite outcome, driven only by where the signal lives.
A rank-1 memory that cross-attends a precomputed windowed velocity \emph{contains} the exact
feature LightGBM turns into \num{0.36}, yet the frozen probe reaches only \num{0.047}: the masked
objective~\cite{devlin2019bert,he2022mae}
has no reason to preserve a feature that does not aid token reconstruction, so a frozen
readout cannot extract it even when it is in the input. We call this the \emph{proxy-alignment
gap}; it explains why bolting relational memory onto a frozen backbone fails.

\paragraph{The cross-sequence encoder recovers the signal --- but raw attention is unstable.}
Trained end-to-end on the relational data (Table~\ref{tab:main}, synthetic column, mean\,$\pm$\,std
over 3 seeds), the per-account FFM sits at $0.039\pm0.004$ and a rank-1 memory at $0.088\pm0.009$
--- both tight. Raw-neighbour cross-sequence attention reaches a much higher \emph{mean}
($0.252\pm0.117$) but is \textbf{wildly seed-unstable} (per-seed $0.41/0.13/0.22$): on a small,
rare-positive set the added attention capacity sometimes finds the burst pattern and sometimes does
not. This instability is the crux of the count-vs-pattern story (\S\ref{sec:method:countaware}):
the \textbf{count-aware} encoder, which adds an always-on velocity readout to the same attention,
is both higher and \emph{stable} ($0.318\pm0.010$) --- the magnitude path anchors the model while
the attention path adds pattern. Here the signal is a neighbour \emph{pattern}, so attention
carries most of the lift; the count path's role is to \emph{stabilise} it.

\paragraph{Why the FFM does not beat the GBDT here --- and why that is the point.} On this
benchmark the GBDT ceiling is above every FFM arm, and deliberately so. The relational signal is,
by construction, a \emph{scalar} cross-card velocity (merchant identity uninformative, amounts
drawn from the legit distribution, fraud cards random); a GBDT handed that one feature is near
optimal on it. Crucially the FFM has \emph{no informational edge} to exploit: because fraud lands
on \emph{random} cards, a card's own history --- the History encoder's forte --- is uninformative,
so the FFM and the GBDT work from the same signal and the FFM only pays a representation and
small-sample optimisation overhead. This is the opposite of TalkingData (\S\ref{sec:realdata}),
where the FFM \emph{does} beat the tabular baseline precisely because it models a user's own click
sequence that the baseline lacks. The GBDT here is not a competitor but the \emph{ceiling} that
certifies the signal is real and strong; the FFM result to read is the \emph{ablation}
($0.039\!\to\!0.318$), i.e.\ that a per-account model is blind to signal the cross-sequence encoder
recovers. Consistent with \S\ref{sec:ffmvsgbdt}, an FFM beats trees only when it carries sequential
structure the tree lacks --- not on a pure count.
