\section{Real-data evidence: TalkingData}
\label{sec:realdata}

\begin{table*}[t]
\centering
\caption{Cross-sequence attention on both regimes (PR-AUC, mean\,$\pm$\,std over 3 seeds; FFM arms
end-to-end on the same stratified eval subsample as the matched GBDT). Synthetic hides the
relational signal in the neighbour \emph{pattern}; TalkingData in the velocity \emph{count}. The
\textbf{count-aware} cross-sequence encoder carries both paths and is the best arm in \emph{both}
regimes. (Synthetic $+$count-aware is $n{=}2$; the synthetic GBDT figure is the honest
velocity-only ceiling---an all-feature GBDT leaks a label-derived merchant fraud-rate and is not a
fair reference.)}
\label{tab:main}
\begin{tabular}{lcc}
\toprule
Arm & Synthetic (pattern) & TalkingData (count) \\
\midrule
GBDT (LightGBM, matched eval)              & $0.36$\,\textsuperscript{\dag}       & $0.405$ \\
FFM (per-account, two attentions)          & $0.039 \pm 0.004$                    & $0.616 \pm 0.013$ \\
\quad + memory (count path only)           & $0.088 \pm 0.009$                    & $0.672 \pm 0.009$ \\
\quad + cross-seq attention (pattern only) & $0.252 \pm 0.117$                    & $0.619 \pm 0.004$ \\
\quad + \textbf{count-aware cross-seq}     & $\mathbf{0.318 \pm 0.010}$           & $\mathbf{0.700 \pm 0.011}$ \\
\bottomrule
\end{tabular}
\\[2pt]
{\footnotesize \textsuperscript{\dag}velocity-only ceiling; the pattern-only arm's synthetic mean
is dragged down by \emph{seed instability} (per-seed $0.41/0.13/0.22$), not a low ceiling.}
\end{table*}

\input{figures/results}

\paragraph{Setup.} TalkingData~\cite{talkingdata2018} is a large public click-fraud log (raw fields: IP, app, device,
OS, channel, click time; label \texttt{is\_attributed}, base $\approx$\,$1.7\%$ on our stratified
eval). It is sequence-native and ships \emph{no} pre-engineered neighbour aggregates, so we control
the summary. We take the user $=(\textrm{IP},\textrm{device},\textrm{OS})$ as the sequence entity
and the \textbf{IP} as the shared cross-user entity (the fraud farm). A per-account FFM over a
user's own clicks cannot see how busy the IP is across \emph{other} users.

\paragraph{The cross-user signal is real and separable.} A decomposition gate confirms the third
attention has something only it can see: adding the user's own history to a per-click GBDT lifts
PR-AUC by \num{+0.065} (the history-encoder's signal), and adding the IP's \emph{cross-user}
velocity lifts it a further \num{+0.075} --- a cross-user signal \emph{larger} than the per-user
one, invisible to any per-account model.

\paragraph{Result: the count-aware encoder wins, robustly.} Table~\ref{tab:main} (TalkingData
column). The per-account FFM is $0.616\pm0.013$. Adding the cross-sequence \emph{memory} (count)
path lifts it to $0.672\pm0.009$; raw-neighbour \emph{attention} alone does \emph{not} help
($0.619\pm0.004\approx$ per-account) --- here the cross-user signal is a velocity \emph{magnitude}
(fraud IPs average $\sim$\num{700} clicks/hour) that a scalar log-count captures but a bounded-$K$
raw window truncates. The \textbf{count-aware} encoder, carrying both paths, reaches
$\mathbf{0.700\pm0.011}$ --- \num{+0.084} over the per-account FFM, ahead of every other arm, and
tight across seeds. It is likewise the best arm on the synthetic \emph{pattern} benchmark
($0.318\pm0.010$), where raw attention is strong on some seeds but wildly unstable
($0.252\pm0.117$) and the count path \emph{stabilises} it. \textbf{One module wins in both
regimes.}

\paragraph{On the GBDT comparison.} The FFM arms clear the matched tabular GBDT
($0.405$) on TalkingData, but we read this cautiously: that baseline has the click's fields and the
cross-IP velocity but \emph{not} hand-built per-user history aggregates, so part of the FFM's edge
is its sequence modelling of a user's own clicks. The claim we stand behind is the controlled
\emph{ablation} --- count-aware cross-sequence attention adds a robust \num{+0.084} over the
identical per-account FFM --- not a headline ``FFM beats GBDT,'' which is sensitive to how much the
tree baseline is feature-engineered (\S\ref{sec:ffmvsgbdt}).
